---
title: "Iteration"
author: "Yifan Shi"
date: "2024-10-24"
output: github_document
---
```{r set up, include=FALSE}
library(tidyverse)
library(rvest)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Here are some lists
```{r}
l = list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
)

l$mat

#this is preferred
l[["mat"]][1, 3]

l[[1]]
```

Make a list that's hopefully a bit more useful

```{r}
list_norm = 
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```

function for mean and sd
```{r}
mean_and_sd = function(x){
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df = 
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(out_df)
}
```

lets use the function to take mean and sd of all samples
```{r}

mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])


```


use a for loop
create output list and run a for loop

```{r}
output = vector("list", length = 4)

for (i in 1:4){
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}

output
```

do the same thing with map
```{r}
output = map(list_norm, mean_and_sd)
```


let's do a couple of other things 
```{r}
output = map(list_norm, IQR)

output = map(list_norm, mean_and_sd) %>% 
  bind_rows()

output = map_dfr(list_norm, mean_and_sd)

output = map_dbl(list_norm, IQR)
```

list columns
```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )

listcol_df

listcol_df %>% 
  filter(name %in% c("a", "b"))

listcol_df %>% 
  select(-samp)

```


```{r}
listcol_df[["samp"]][["a"]]

```

compute mean and sd

```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])
mean_and_sd(listcol_df[["samp"]][["b"]])

map(listcol_df[["samp"]], mean_and_sd)
```


add a list column

```{r}
listcol_df %>% 
  mutate(output = map(samp, mean_and_sd),
         iqr = map_dbl(samp, IQR))

listcol_df %>% 
  mutate(output = map(samp, mean_and_sd),
         iqr = map_dbl(samp, IQR)) %>% 
  select(-samp) %>% 
  unnest(output)
```


NSDUH dataset

this is a version of our function last time
```{r}
drug_table = function(html, table_num){
  
  drug_df = 
    html %>% 
    html_table() %>% 
    nth(table_num) %>% 
    slice(-1) %>% 
    select(-contains("P Values"))
  
  return(drug_df)
  
}
```

we need to import the html, and then extract the correct table

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```


```{r}
drug_table(html = nsduh_html, table_num = 1)
drug_table(html = nsduh_html, table_num = 4)
drug_table(html = nsduh_html, table_num = 5)
```

```{r}
nsduh_df = 
  tibble(
    drug = c("marj", "cocaine", "herion"),
    table_n = c(1, 4, 5)
  ) %>% 
  mutate(table = map(table_n, drug_table, html = nsduh_html)) %>% 
  unnest(table)

nsduh_df = 
  tibble(
    drug = c("marj", "cocaine", "herion"),
    table_n = c(1, 4, 5)
  ) %>% 
  mutate(table = 
           map(table_n,\(x) drug_table(html = nsduh_html, table_num = x))) %>% 
  unnest(table)


nsduh_df %>% 
  filter(State == "New York")
```


